Cluster Difference Imaging Photometric Survey. I. Light Curves of Stars in Open Clusters from TESS Sectors 6 \& 7

### 2019-09-30 paper_I/ms.tex
update received accepted args
cdips-I: link fixing

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass[12pt,twocolumn,tighten]{aastex62}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}

@@

\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
\newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) is providing
  precise time-series photometry for most star clusters in the solar
  neighborhood.
  % Aims
  Using the TESS images, we have begun a Cluster Difference Imaging
  Photometric Survey (CDIPS), in which we are focusing both on stars
  that are candidate cluster members, and on stars that show
  indications of youth.
  %
  Our aims are to discover giant transiting planets with known ages,
  and to provide light curves suitable for studies in stellar
  astrophysics.
  %
  For this work, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.  Each light curve
  represents between 20 and 25 days of observations of a star brighter
  than $G_{Rp}=16$, with 30-minute sampling.
  % Methods
  We describe the image subtraction and time-series analysis
  techniques we used to create the light curves, which have noise
  properties that agree with theoretical expectations.
  %
  We also comment on the possible utility of the light curve sample
  for studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves, which cover about one sixth of the galactic plane,
  are available at \stscilink.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.pdf}{0.42\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to the $N_{\rm total}=1{,}061{,}446$ target stars, which are listed in
		Table~\ref{tbl:cdips_targets}. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main-sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

Figure~\ref{fig:lcgalactic} shows the on-sky locations of the light
curves from Sectors 6 and 7.  Black points are the field stars for
which we performed photometry in order to construct basis vector sets
for TFA and PCA.  Blue points are the \numberlcs target stars for
which light curves are available at \stscilink.  Most of the target
stars are close to the galactic plane, and are spatially clustered.
Gaps between CCD chips are also visible.

@@

In future work, these concerns will likely drive us to expand beyond
the current sample of target stars.  For the time being, the light
curves are of sufficient quality and quantity to begin astrophysical
studies.  We invite any who wish to explore the time evolution of
stellar or exoplanetary systems to interact with the data at
\stscilink.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{comment}

@@

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 18, 2019}
\revised{September 20, 2019}
\accepted{September 23, 2019}
\submitjournal{{\it The Astrophysical Journal Supplement}}

@@

\newcommand{\stscilink}{\textsc{\url{archive.stsci.edu/hlsp/cdips}}}
\newcommand{\stscivetlink}{\url{archive.stsci.edu/prepds/cdips/vetting}}
\newcommand{\datasetlink}{\textsc{\dataset[doi.org/10.17909/t9-ayd0-k727]{https://doi.org/10.17909/t9-ayd0-k727}}}

@@

\begin{abstract}
  % Context
  The Transiting Exoplanet Survey Satellite (TESS) is providing
  precise time-series photometry for most star clusters in the solar
  neighborhood.
  % Aims
  Using the TESS images, we have begun a Cluster Difference Imaging
  Photometric Survey (CDIPS), in which we are focusing both on stars
  that are candidate cluster members, and on stars that show
  indications of youth.
  %
  Our aims are to discover giant transiting planets with known ages,
  and to provide light curves suitable for studies in stellar
  astrophysics.
  %
  For this work, we made \numberlcs light curves of candidate young
  stars, across \numberclusters distinct clusters.  Each light curve
  represents between 20 and 25 days of observations of a star brighter
  than $G_{\rm Rp}=16$, with 30-minute sampling.
  % Methods
  We describe the image subtraction and time-series analysis
  techniques we used to create the light curves, which have noise
  properties that agree with theoretical expectations.
  %
  We also comment on the possible utility of the light curve sample
  for studies of stellar rotation evolution, and binary eccentricity
  damping.
  %
  The light curves\footnote{\stscilink}, which cover about one
  sixth of the galactic plane, are available as a High Level Science
  Product at MAST: \datasetlink.
\end{abstract}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\gridline{\fig{target_star_cumulative_counts.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_hist_logt.pdf}{0.42\textwidth}{}}
		\vspace{-0.8cm}
		\gridline{\fig{target_star_reference_pie_chart.png}{0.42\textwidth}{}}
	\end{center}
	\vspace{-0.8cm}
	\caption{
		Target star statistics.
		{\it Top.} Cumulative counts as a function of apparent Gaia $Rp$-band
		magnitude.  
		{\it Middle.} Histogram of target star ages, for the subset of
		stars with ages matched against \citet{Kharchenko_et_al_2013}.
		{\it Bottom.} Provenance of cluster membership.  Percentages are
		relative to the $N_{\rm total}=1{,}061{,}446$ target stars, which are listed in
		Table~\ref{tbl:cdips_targets}. Symbols
		are as follows.
		D14 is \citet{dias_proper_2014}.
		K13 is \citet{Kharchenko_et_al_2013}.
		CG18 is \citet{cantat-gaudin_gaia_2018}.
		Z18 is \citet{zari_3d_2018}, with upper main-sequence and
		pre-main-sequence samples sub-divided.
		``$\geq 2$'' indicates at least two authors reported a star as a
		candidate cluster member.
		%``Other'' refers to sources enumerated in \S~\ref{sec:starselection}.
		\label{fig:cdips_targets}
	}
\end{figure}

@@

Figure~\ref{fig:lcgalactic} shows the on-sky locations of the light
curves from Sectors 6 and 7.  Black points are the field stars for
which we performed photometry in order to construct basis vector sets
for TFA and PCA.  Blue points are the \numberlcs target stars for
which light curves are available at \datasetlink.  Most of the target
stars are close to the galactic plane, and are spatially clustered.
Gaps between CCD chips are also visible.

@@

In future work, these concerns will likely drive us to expand beyond
the current sample of target stars.  For the time being, the light
curves are of sufficient quality and quantity to begin astrophysical
studies.  We invite any who wish to explore the time evolution of
stellar or exoplanetary systems to interact with the
data\footnote{\stscilink} at \datasetlink.
